Security Audit of Safeplug ``Tor in a Box''

### 2014-02-28 w2sp/report.tex
made some suggested changes and added TODO file

@@

Privacy on the Internet is becoming increasingly important as more users realize how vulnerable they are to surveillance and attacks; anonymity has become the goal for many Internet users in order to protect themselves.  A recent study has shown that people have been the victim of many security-related issues, such as compromised emails/accounts, harrassment, stolen Social Security Numbers, bank information, and credit card numbers, due to their online visibility~\cite{pew}.  As the Internet grows and the amount of user information that is collected and/or provided online increases, users will continue to be more vulnerable.  According to this study, 86\% of internet users have tried to become more anonymous online by either clearing cookies, encrypting their email, or using virtual networks that mask their IP address~\cite{pew}.  While this study shows that a large percentage of users are taking measures to reduce their visibility online, 59\% reported that they don't believe it is possible to become completely anonymous online~\cite{pew}.

@@

\begin{itemize}
\item The Safeplug functions as a HTTP proxy inside the browser, which then uses Tor on outgoing traffic (see Figure \ref{fig:flow}).
\item The presence of both first- and third-party tracking cookies, de-anonymizing users across websites despite the presence of Tor.
\item A Cross-Site Request Forgery (CSRF) vulnerability that allows an outside attacker to modify the Safeplug settings (i.e., turning Tor on/off, turning ad-blocking on/off, turning the Tor relay setting on/off, adding/removing whitelisted sites from Tor).
\item A vulnerability that allows an attacker within the network to modify the Safeplug settings without notifying any other devices on the network.
\item A higher latency than that of the Tor Browser Bundle.
\end{itemize}

@@

\begin{figure*}
\centering
\includegraphics[width=.75\textwidth]{instructions}
\caption{Setup instructions (and the only documentation) that came in the box with the Safeplug. Pogoplug highlights the ease of installing the device but does not give a clear indication of how the Safeplug functions.}
\label{fig:instructions}
\end{figure*}

@@

{\bf Pogoplug.} Pogoplug, a subsidary of Cloud Engines, also offers a box for home network file sharing without needing to use a third-party storage provider.  Based on our examination of the box discussed below, we suspect that the Pogoplug box was relabelled as Safeplug and simply uses different software to achieve its newly branded purpose.

@@

\subsection{Information Prior to Using the Device: Terms of Service}
\label{tos}
The Terms of Service (TOS) contains three main points of interest: TOS updates, open source licensing information, and software updates.  First, the TOS are not presented to the user in the Safeplug package (the only information in the packaging were the instructions shown in Figure~\ref{fig:instructions}) or during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.  Although use of the Safeplug device constitutes acceptance of the TOS, most users are not likely to read the TOS even once.  However, Pogoplug suggests that users regularly review the TOS because they can update or change them at any time; this is standard language in TOS but not a good combination with them not being presented to the user.

@@

\subsection{Cookies}  
While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ widget in a different tab.  When we clicked on the Google+ widget, it remember who we are; so we can confirm that we still have first-party cookies.  We experienced the same situation with Facebook and its corresponding ``like'' button.  This was confirmed by using FourthParty, a plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data.

@@

\section{Conclusion}
Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is not the correct method for security and anonymity online.  It is critical for Safeplug to correct their engineering errors, particularly the vulnerability to silently disable Tor, in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.

>>>>

\pagestyle{plain}

@@

Privacy on the Internet is becoming increasingly important as more users realize how vulnerable they are to surveillance and attacks; anonymity has become the goal for many Internet users in order to protect themselves.  A recent study has shown that people have been the victim of many security-related issues, such as compromised emails/accounts, harrassment, stolen Social Security Numbers, bank information, and credit card numbers, due to their online visibility~\cite{pew}.  As the Internet grows and the amount of user information that is collected and/or provided online increases, users will continue to be more vulnerable.  According to one study, 86\% of internet users have tried to become more anonymous online by either clearing cookies, encrypting their email, or using virtual networks that mask their IP address~\cite{pew}.  While this study shows that a large percentage of users are taking measures to reduce their visibility online, 59\% reported that they don't believe it is possible to become completely anonymous online~\cite{pew}.

@@

\begin{itemize}
\item The Safeplug functions as a HTTP proxy for the browser, which then uses Tor on outgoing traffic (see Figure \ref{fig:flow}).
\item The presence of both first- and third-party tracking cookies, de-anonymizing users across websites despite the presence of Tor.
\item A Cross-Site Request Forgery (CSRF) vulnerability that allows an outside attacker to modify the Safeplug settings (i.e., turning Tor on/off, turning ad-blocking on/off, turning the Tor relay setting on/off, adding/removing whitelisted sites from Tor).
\item A vulnerability that allows an attacker within the network to modify the Safeplug settings without notifying any other devices on the network.
\item A higher latency than that of the Tor Browser Bundle.
\end{itemize}

@@

\begin{figure*}
\centering
\includegraphics[width=.75\textwidth]{instructions2}
\caption{Setup instructions (and the only documentation) that came in the box with the Safeplug. Pogoplug highlights the ease of installing the device but does not give a clear indication of how the Safeplug functions.}
\label{fig:instructions}
\end{figure*}

@@

{\bf Pogoplug.} Pogoplug, a subsidary of Cloud Engines, also offers a box for home network file sharing without needing to use a third-party storage provider.  Based on our examination of the box discussed below, we suspect that the Pogoplug hardware was relabelled as Safeplug and simply uses different software to achieve its newly branded purpose.

@@

\subsection{Information Prior to Using the Device: Terms of Service}
\label{tos}
The Terms of Service (TOS) contains three main points of interest: TOS updates, open source licensing information, and software updates.  First, the TOS are not presented to the user in the Safeplug package (the only information in the packaging were the instructions shown in Figure~\ref{fig:instructions}) or during the activation process, and are only available through a small link at the bottom of the Safeplug website\cite{safeplug}.  Although use of the Safeplug device purportedly constitutes acceptance of the TOS, most users are not likely to read the TOS even once.  However, Pogoplug suggests that users regularly review the TOS because they can update or change them at any time; this is standard language in TOS but not a good combination with them not being presented to the user.

@@

\subsection{Cookies}  
While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ widget in a different tab.  When we clicked on the Google+ widget, it remember who we are; so we can confirm that a cookie associated with the login was sent to the second Google+ page.  We experienced the same situation with Facebook and its corresponding ``like'' button.  This was confirmed by using FourthParty, a plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data.

@@

\section{Conclusion}
Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is problematic as a method for security and anonymity online.  It is critical for Safeplug to correct their engineering errors, particularly the vulnerability to silently disable Tor, in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.
